Quantifying the global film festival circuit: networks, diversity and value creation

### 2023-04-23 cudan/paperplots.qmd
dashboard

# Festival_de_Cannes - Big 5 example (A)
# Sundance - Big 5 example (B)
# Hot_Docs_Festival - Genre - Doc example (B)
# Sitges_FF - Genre - fantasy & horror example (A)
# Busan_IFF - Geo - Asian example (A)
# BAFICI - Geo - Latin American example (B)

@@

# gender examples TODO------- aside from Cannes and Sundance (and instead of Hot Docs and Sitges), could we please have SXSW for B and Berlinale for A

allfests = nodelist %>% group_by(libelleFestival_NEW_VZ) %>% filter(n()>3) %>% pull(libelleFestival_NEW_VZ) %>% unique

@@

divyearplot = function(vecs, ex, shape=16, yl="", splitab=T, convert=T, networkstats=T, ylims=NULL, genrecols=sixgcols, pies=NULL, nrowmod=6){
  if(splitab){
    vecs = vecs %>% mutate(YearEvent=case_when(ab=="A"~YearEvent-0.15,
                                               ab=="B"~YearEvent+0.15 )) %>% 
      arrange(libelleFestival_NEW_VZ) %>% 
      mutate(series = substr(libelleFestival_NEW_VZ, 1,15))
    if(length(unique(vecs$libelleFestival_NEW_VZ)) != 
       length(unique(vecs$series))){ stop("shortening mismatch")}
    vex=vecs
    g=ggplot(vecs , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  } else {
     vex = vecs %>% 
       filter(libelleFestival_NEW_VZ %in% ex, !is.na(target)) %>% 
       mutate(libelleFestival_NEW_VZ=fct_relevel(libelleFestival_NEW_VZ, ex))
     g=ggplot(vex , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  }

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray40", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = ceiling(length(ex)/nrowmod))+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray60", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       panel.grid.minor.y  = element_blank(),
       legend.position = 'none',
       strip.text = element_text(hjust=0, margin=margin(0.5,0,0.5,1))
       )

@@

    }
  }

  minx = min(vex$YearEvent, na.rm=T)
  if(!is.null(ylims)){
    g=g+
      coord_cartesian(ylim = ylims, expand=F)+
      scale_x_continuous(breaks=seq(minx+1,2020,3), limits=c(minx-0.4,2021+0.4 ) )
  } else {
    g=g+ scale_x_continuous(breaks=seq(minx+1,2020,3), expand = expansion(0.1,0) )+
      scale_y_continuous(expand=c(0.05,0)
        #limits=c( min(c(vecs$target, vecs$lower), na.rm=T), max(c(vecs$target, vecs$upper), na.rm=T )*1.001 )
        )
  }

@@

# festival illustration squares.
ggplot(tops, aes( x=s,y=libelleFestival_NEW_VZ, fill=colorgenre2))+
  geom_bar(stat="identity", color=NA,position="stack")+
  scale_fill_manual(values=
                      c(sixgcols %>% head(-1),
                        gray.colors(
                          length(unique(tops$colorgenre2))-
                            length(mains),
                          start=0.5, end=0.7
                          )) %>% rev)+
  coord_cartesian(expand = 0, xlim=c(0,100))+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "none",
        panel.border  = element_rect(linewidth=0.5, color="gray10", fill=NA)
        )+
  facet_wrap(~libelleFestival_NEW_VZ, strip.position="bottom", scales = "free", nrow=2)

@@

ggplot(attr(genlat, "latmap"), aes(V1,V2,label=txtKind,size=n))+geom_text()+
  scale_size(range=c(1.5,5))+
  theme_void()+
  theme(legend.position = "none",
        panel.border = element_rect(fill=NA)
        )

@@

Also, note the error bars: they represent 95% confidence intervals from a nonparametric bootstrapping, i.e. the true mean value (the dots) are likely to be within the given range. Smaller festival samples and festivals with more variation around the mean for a given statistic therefore have larger bar ranges. While not quite equivalent to a pairwise significance test, as a rule of thumb, if the intervals of two points of interest overlap more (more than just a bit; intervals are more conservative than pairwise tests), then the difference is likely not statistically significant.

@@

-   Event time distance is more of a control, as we know films circulate for a few years usually (the negative $\beta$ coefficient estimate means that the more the two festivals are apart in time, the less likely they are to share films - makes sense).
-   The class categorical variable baseline is that the pair is of different type, so if both are A and A, they are more likely to share a film; if both are B, then they are less likely to share (note the imbalance though, theres more all sorts of B fests)
-   All the other distances are also negative: e.g. the more the mean content/genre vectors differ (higher content distance), the less likely they are to share films (again makes sense).
-   The only one is event location distance - here, festivals are more likely to share films if they are *further* away from each other - I suppose filmmakers want to travel the world with their films, and not stick to the same region? But this effect may also vary between regions themselves, or content types, or who knows what else (which could be further modelled and measured of course).

Given suitable hypotheses, could also test interactions. Importantly, this modelling is all based on festival means, and individual films are not taken into account - but it could also be done this way, to model the likelyhood that a pair of films share a festival (instead of a pair of festivals sharing a film), which might make more sense.

```{r}
library(rms)
options(scipen=999)
# linkdat = linkdat %>% mutate(class2 = case_match(class, ))
table(linkdat$linked)
glm(linked~timedist+ eventdist+ class ,family = "binomial", 
        data=linkdat %>% select(-weight) %>% {.[complete.cases(.),]} %>% 
      mutate(class2=relevel(as.factor(class), "_bothBB"))
    ) %>% summary %>% print
lrm(linked~timedist+ eventdist+ class , data=linkdat)
# glm(linked~timedist+ eventdist* class ,family = "binomial", 
#         data=linkdat %>% select(-weight) %>% {.[complete.cases(.),]} %>% 
#       mutate(class2=relevel(as.factor(class), "_bothBB"))
#     ) %>% summary %>% print

@@

# Mcfadden's:
1 - ( 
      as.numeric(logLik(glm(weight~timedist+eventdist+class, 
        data=linkdat %>% filter(weight>0) %>% {.[complete.cases(.),]},
    family = poisson(link = "log")))) /

@@

@@

ggplot( aes(V1,V2,label=txtKind2, size=log(n)))+
  geom_text_repel( box.padding = 0, min.segment.length = 9999, max.time = 5, max.overlaps = 1000000)+
  scale_size(range=c(1.6,3))+
  theme_void()+
  theme(legend.position = "none",
        panel.border = element_rect(fill=NA)
        )
```

@@

fig_change = divyearplot(genrechangevals %>% 
              mutate(target=dif, lower=diflower, upper=difupper), 
            ex=exchange, 
            yl="Yearly change", ylims = c(-0.005,0.09),
            convert=convertplots, splitab=F, networkstats = F, 
            genrecols = sixgcols, 
            pies=attr(festgenrevecs, "tops"),
            nrowmod=1
            )+
  scale_y_continuous(breaks=c(0,0.04,0.08))+
  geom_path(aes(YearEvent, target), data=genrechangevals %>%
              filter(libelleFestival_NEW_VZ==exchange[1]) %>%  
              mutate(target=dif), inherit.aes=F)+
  labs(tag="B")+
  theme(plot.tag=element_text(face = "bold",hjust=1,vjust=1, margin=margin(-5,-9,-11,0)), 
        plot.margin = margin(1,1,0,0))+theme(axis.title.y=element_blank())

@@

@@

# content space with change plots

lm(indiv~ab, festlangvecs, weights=nf) %>% summary()
lm(indiv~ab, festlangvecs, weights=nf) %>% summary()

lm(ratiofmin~ab, festrolevecs) %>% summary()
lm(ratiofmax~ab, festrolevecs) %>% summary()
lm(ratiof~ab, festrolevecs, weights=nf) %>% summary() # gender

@@

festrolevecs %>% filter(grepl("SXSW", libelleFestival_NEW_VZ) ) %>% as.data.frame() %>% arrange(YearEvent)

festrolevecs %>% filter(grepl("Sundance", libelleFestival_NEW_VZ) ) %>% as.data.frame() %>% arrange(YearEvent)

attr(festrolevecs, "sysdivs")

@@

dat = fesfilm2 %>% 
    rename(nsort=nroles) %>%  # variable passing now works
    mutate(tmp=paste0(TitleVA, "_", YearOfProduction )) %>% 
    group_by(EventID_VZ) %>%   # for duplicate film removal
    arrange(desc(nsort), is.na(YearOfProduction), .by_group = T) %>%  # prefer more complete entries
    filter(!duplicated(tmp)) %>%  # remove duplicate films within event (works, w ungroup fewer rows)
    group_by(EventID_VZ) %>% filter(n()>=15) %>% 
    ungroup() %>% 
    left_join(filmrole, by = "refFilm", multiple = "all") %>% 
  filter(txtKind!="other") %>% 
    group_by(EventID_VZ) %>% 
      mutate(nf=n_distinct(refFilm)) %>% 
       filter(nf>=15) %>% 
  mutate(txtKind=as.factor(txtKind), txtType=as.factor(txtType))

@@

plotbees = function(vecs, tag, tlab="", col=NULL, cex=3, vw=1.7){
  g=ggplot(vecs, aes(x=as.factor(ab) %>% as.numeric , group=as.factor(ab) %>% as.numeric, color=ab,y=target))+
  #geom_boxplot(fill=NA, color="gray30", width=0.2)+
  geom_violin(fill=NA, color="gray50", size=0.1,scale="count", width=vw)

  if(is.null(col)){
    g=g+geom_beeswarm(aes(color=ab), cex = cex,priority = "random",size=0.5)
  } else {
    g=g+geom_beeswarm(color=col, cex = cex,priority = "random",size=0.5)
  }

  g=g+stat_summary(na.rm=T, shape="-", color="black", fun = median, size=2)+
  #scale_shape_manual(values=abshapes)+
  scale_color_manual(values=abcols)+
  scale_size_manual(values=c(0.6,0.3))+
  coord_cartesian(xlim=c(0.6,2.6), expand=T)+
  labs(title = expr(paste(bold(!!tag), !!tlab)))+
  scale_x_continuous(breaks=1:2, labels=c("A", "B"))+
  scale_y_continuous(expand=expansion(0.01,0))+
  theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title = element_blank(),
        plot.margin = margin(1,1,1,1),
        plot.title = element_text(size=8, margin=margin(0,0,0,0)),
        legend.position = "none",
        axis.text.x = element_text(size=6, margin=margin(-1,0,0,0), vjust=1),
        axis.text.y = element_text(size=6, margin=margin(0,-1,0,0), hjust=1),
        axis.ticks = element_blank()
        )
}

@@

fig_gex = divyearplot(festrolevecs  %>% mutate(target=ratiof, lower=rfminboot, upper=rfmaxboot),
            ex=exrolefests, yl="% of women", convert=convertplots, splitab=F, networkstats = F, ylims=c(0,0.59), nrowmod = 2)+theme(axis.title = element_blank())

@@

fig_thematic_div = 
  (tags(sysplots(attr(festgenrevecs,"sysdivs"), yl="Circuit thematic diversity")+
          theme(legend.position = c(0.85,0.22), legend.title = element_blank()),"A") +
  tags(divyearplot(festgenrevecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgenfests, yl="Internal thematic diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies = pies2, genrecols = sixgcols), "B")
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))

@@

tbees = 
  plotbees(festcountryvecs %>% mutate(target=indiv), "C", tlab=" Internal", col="gray50", cex=3, vw = 1.5) +
  plotbees(festcountryvecs %>% mutate(target=exdiv), "D", tlab=" Contributing", col="gray50", cex=2.9, vw=1.4)+plot_layout(nrow=2)

@@

fig_geo_div = 
  (tags(sysplots(attr(festcountryvecs,"sysdivs"), yl="Circuit geographic diversity")+
          theme(legend.position = c(0.6,0.22), legend.title = element_blank()),"A") +
  tags(divyearplot(festcountryvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgeofests, yl="Internal geographic diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies=piesg, genrecols = sixcols), "B")
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))+
  plot_annotation(theme=theme(plot.margin=margin(0,0,0,0)))

@@

fig_lang_div = 
  (tags(sysplots(attr(festlangvecs,"sysdivs"), yl="Circuit language diversity")+
          theme(legend.position = c(0.75,0.1),legend.direction = "horizontal", legend.title = element_blank()),"A") +
  tags(divyearplot(festlangvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exlangfests, yl="Internal language diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies=piesl, genrecols = langcols), "B")
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))

@@

@@

>>>>

@@

# allfests = nodelist %>% group_by(libelleFestival_NEW_VZ) %>% filter(n()>3) %>% pull(libelleFestival_NEW_VZ) %>% unique

@@

divyearplot = function(vecs, ex, shape=16, yl="", splitab=T, convert=T, networkstats=T, ylims=NULL, genrecols=sixgcols, pies=NULL, nrowmod=6, contrdiv=T){
  if(splitab){
    vecs = vecs %>% mutate(YearEvent=case_when(ab=="A"~YearEvent-0.15,
                                               ab=="B"~YearEvent+0.15 )) %>% 
      arrange(libelleFestival_NEW_VZ) %>% 
      mutate(series = substr(libelleFestival_NEW_VZ, 1,15))
    if(length(unique(vecs$libelleFestival_NEW_VZ)) != 
       length(unique(vecs$series))){ stop("shortening mismatch")}
    vex=vecs
    g=ggplot(vecs , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  } else {
     vex = vecs %>% 
       filter(libelleFestival_NEW_VZ %in% ex, !is.na(target)) %>% 
       mutate(libelleFestival_NEW_VZ=fct_relevel(libelleFestival_NEW_VZ, ex))
     g=ggplot(vex , 
        aes(YearEvent, target, color=ab, shape=ab,  text=tool))
  }

@@

  if(!splitab & !is.null(ex)){
   if(networkstats){
      fromy=2014.5; toy=2019.5
    } else{
      fromy=2008; toy=2022
      g=g+geom_errorbar(aes(ymin=lower, ymax=upper), color="gray30", width=0.1, size=0.45)
    }
    g=
      g+facet_wrap(~libelleFestival_NEW_VZ, nrow = ceiling(length(ex)/nrowmod))+
      # geom_point( aes(YearEvent, target),data=vecs %>% select(-libelleFestival_NEW_VZ), inherit.aes = F,
      #             color="gray90", size=0.9)+
      geom_line(data=vex %>% filter(YearEvent>fromy, YearEvent<toy) %>% 
                  group_by(YearEvent, libelleFestival_NEW_VZ) %>% 
                  summarise(target=mean(target, na.rm=T), tool=NA, ab=ab[1]), 
                color="gray70", size=0.3
                )+
      geom_point(data=vex, alpha=1, size=1.5, shape=16)+
      theme(
       panel.grid.major.x  = element_line(color="gray95"),
       panel.grid.minor.x  = element_blank(),
       panel.grid.minor.y  = element_blank(),
       legend.position = 'none',
       strip.text = element_text(hjust=0, margin=margin(0.5,0,0.5,1))
       )

@@

    }
    if(contrdiv){
      g = g+geom_errorbar(aes(ymin=elower, ymax=eupper), color="gray60", width=0, size=0.45,
                          position=position_nudge(0.45))+
        geom_point(aes(y=exdiv), color="gray60", size=0.5, shape=15, 
                   position=position_nudge(0.45))+
        theme(axis.title.y.right = element_text(color="gray50"), 
              axis.ticks.length.y.right = unit(0,"in"),
              axis.text.y.right = element_blank())
    }
  }

  minx = min(vex$YearEvent, na.rm=T)
  if(!is.null(ylims)){
    g=g+
      coord_cartesian(ylim = ylims, expand=F)+
      scale_x_continuous(breaks=seq(minx+1,2020,3), limits=c(minx-0.4,2021+0.4 ) )
  } else {
    g=g+ scale_x_continuous(breaks=seq(minx+1,2020,3), expand = expansion(0.1,0) )+
      scale_y_continuous(expand=c(0.05,0)
        #limits=c( min(c(vecs$target, vecs$lower), na.rm=T), max(c(vecs$target, vecs$upper), na.rm=T )*1.001 )
        )
        if(contrdiv){
          g=g+scale_y_continuous(expand=c(0.05,0),sec.axis = sec_axis(~., name="Contributing diversity"))
        }
  }

@@

# festival illustration squares.
ggplot(tops, aes( y=s,x=colorgenre2, fill=colorgenre2))+
  geom_bar(stat="identity", color=NA)+
  scale_fill_manual(values=
                      c(sixgcols %>% head(-1),
                        gray.colors(
                          length(unique(tops$colorgenre2))-
                            length(mains),
                          start=0.5, end=0.7
                          )) %>% rev)+
  coord_cartesian(expand = 0)+
  scale_x_discrete(breaks=mains)+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "none",
        panel.border  = element_rect(linewidth=0.5, color="gray10", fill=NA), 
        strip.text = element_text(size=15),
        plot.margin = margin(3,3,3,3)
        )+
  facet_wrap(~libelleFestival_NEW_VZ, strip.position="top",  nrow=2)

@@

ggplot(attr(genlat, "latmap"), aes(V1,V2,label=txtKind,size=n))+geom_text()+
  scale_size(range=c(1.5,5))+
  theme_void()+
  theme(legend.position = "none",
        panel.border = element_rect(fill=NA),
        plot.margin = margin(1,1,1,1)
        )
ggsave("fig_sup_latentmap.pdf", width=9, height=5, scale=0.6)

@@

Also, note the error bars: they represent 95% confidence intervals from a nonparametric bootstrapping, i.e. the true mean value (the dots) are likely to be within the given range. Smaller festival samples and festivals with more variation around the mean for a given statistic therefore have larger bar ranges.

@@

-   Event time distance is more of a control, as we know films circulate for a few years usually (the negative $\beta$ coefficient estimate means that the more the two festivals are apart in time, the less likely they are to share films - makes sense).
-   The class categorical variable baseline is that the pair is of different type, so if both are A and A, they are more likely to share a film; if both are B, then they are less likely to share (note the imbalance though, theres more all sorts of B fests)

```{r}
library(rms)
options(scipen=999)
# linkdat = linkdat %>% mutate(class2 = case_match(class, ))
table(linkdat$linked)
m = glm(linked~timedist+ eventdist+ class ,family = "binomial", 
        data=linkdat %>% select(-weight) %>% {.[complete.cases(.),]} %>% 
      mutate(class2=relevel(as.factor(class), "_bothBB"))
    )

m %>% summary %>% print

cbind(m$coefficients,
      m$coefficients %>% exp,
      round(summary(m)$coefficients[,"Pr(>|z|)"], 4))

lrm(linked~timedist+ eventdist+ class , data=linkdat)
# glm(linked~timedist+ eventdist* class ,family = "binomial", 
#         data=linkdat %>% select(-weight) %>% {.[complete.cases(.),]} %>% 
#       mutate(class2=relevel(as.factor(class), "_bothBB"))
#     ) %>% summary %>% print

@@

linkdat %>% filter(weight>0) %>% nrow
# Mcfadden's:
1 - ( 
      as.numeric(logLik(glm(weight~timedist+eventdist+class, 
        data=linkdat %>% filter(weight>0) %>% {.[complete.cases(.),]},
    family = poisson(link = "log")))) /

@@

cbind(m$coefficients,
      m$coefficients %>% exp, 
      round(summary(m)$coefficients[,"Pr(>|z|)"], 4))

@@

@@

fig_change = divyearplot(genrechangevals %>% 
              mutate(target=dif, lower=diflower, upper=difupper), 
            ex=exchange, 
            yl="Yearly change", ylims = c(-0.005,0.09),
            convert=convertplots, splitab=F, networkstats = F, 
            genrecols = sixgcols, 
            pies=attr(festgenrevecs, "tops"),
            nrowmod=1, contrdiv = F
            )+
  scale_y_continuous(breaks=c(0,0.04,0.08))+
  geom_path(aes(YearEvent, target), data=genrechangevals %>%
              filter(libelleFestival_NEW_VZ==exchange[1]) %>%  
              mutate(target=dif), inherit.aes=F)+
  labs(tag="B")+
  theme(plot.tag=element_text(face = "bold",hjust=1,vjust=1, margin=margin(-5,-9,-11,0)), 
        plot.margin = margin(1,1,0,0))+theme(axis.title.y=element_blank())

@@

## Regressions

@@

# intercept only prod-dir

@@

attr(festrolevecs, "sysdivs") %>% filter(YearEvent %in% c(2012,2021))

lm(ratiof~ab, festrolevecs, weights=nf) %>% summary() # gender

festrolevecs %>% filter(grepl("Sundance", libelleFestival_NEW_VZ) ) %>% as.data.frame() %>% arrange(YearEvent) %>% select(rfminboot, rfmaxboot)
festrolevecs %>% filter(grepl("SXSW", libelleFestival_NEW_VZ) ) %>% as.data.frame() %>% arrange(YearEvent) %>% select(rfminboot, rfmaxboot)

# language, AB
lm(indiv~ab, festlangvecs, weights=nf) %>% summary()

# series
nodelist %>% group_by(libelleFestival_NEW_VZ) %>% filter(n_distinct(EventID_VZ)>=2) %>% pull(libelleFestival_NEW_VZ) %>% unique %>% length
nodelist %>% group_by(libelleFestival_NEW_VZ) %>% filter(n_distinct(EventID_VZ)<2) %>% pull(libelleFestival_NEW_VZ) %>% unique %>% length

# gender, AB
lm(ratiofmin~ab, festrolevecs) %>% summary()
lm(ratiofmax~ab, festrolevecs) %>% summary()
lm(ratiof~ab, festrolevecs, weights=nf) %>% summary() # gender

@@

dat = fesfilm2 %>% 
    rename(nsort=nroles) %>%  
    mutate(tmp=paste0(TitleVA, "_", YearOfProduction )) %>% 
    group_by(EventID_VZ) %>%   # for duplicate film removal
    arrange(desc(nsort), is.na(YearOfProduction), .by_group = T) %>%  # prefer more complete entries
    filter(!duplicated(tmp)) %>%  # remove duplicate films within event (works, w ungroup fewer rows)
    group_by(EventID_VZ) %>% filter(n()>=15) %>% 
    ungroup() %>% 
    left_join(filmrole, by = "refFilm", multiple = "all") %>% 
  filter(txtKind!="other") %>% 
    group_by(EventID_VZ) %>% 
      mutate(nf=n_distinct(refFilm)) %>% 
       filter(nf>=15) %>% 
  mutate(txtKind=as.factor(txtKind), txtType=as.factor(txtType))

@@

plotbees = function(vecs, tag, tlab="", col=NULL, cex=3, vw=1.7, comp=F, colvals=abcols){
  g=ggplot(vecs %>% 
             mutate(comp=case_when(
               `PFIAF category`=="Competitive Feature Film Festivals"~"comp", T~"no"
               )), 
           aes(x=as.factor(ab) %>% as.numeric , group=as.factor(ab) %>% as.numeric, color=ab,y=target))+
  #geom_boxplot(fill=NA, color="gray30", width=0.2)+
  geom_violin(fill=NA, color="gray50", size=0.1,scale="count", width=vw)

  if(is.null(col)){
    if(!comp) {g=g+geom_beeswarm(aes(color=ab), cex = cex,priority = "random",size=0.5)}
    if(comp) {g=g+geom_beeswarm(aes(color=comp), cex = cex,priority = "random",size=0.5)}
  } else {
    g=g+geom_beeswarm(color=col, cex = cex,priority = "random",size=0.5)
  }

  g=g+stat_summary(na.rm=T, shape="-", color="black", fun = median, size=2)+
  #scale_shape_manual(values=abshapes)+
  scale_color_manual(values=colvals)+
  scale_size_manual(values=c(0.6,0.3))+
  coord_cartesian(xlim=c(0.6,2.6), expand=T)+
  labs(title = expr(paste(bold(!!tag), !!tlab)))+
  scale_x_continuous(breaks=1:2, labels=c("A", "B"))+
  scale_y_continuous(expand=expansion(0.01,0))+
  theme_bw()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.title = element_blank(),
        plot.margin = margin(1,1,1,1),
        plot.title = element_text(size=8, margin=margin(0,0,0,0)),
        legend.position = "none",
        axis.text.x = element_text(size=6, margin=margin(-1,0,0,0), vjust=1),
        axis.text.y = element_text(size=6, margin=margin(0,-1,0,0), hjust=1),
        axis.ticks = element_blank()
        )
}

@@

fig_gex = divyearplot(festrolevecs  %>% mutate(target=ratiof, lower=rfminboot, upper=rfmaxboot),
            ex=exrolefests, yl="% of women", convert=convertplots, splitab=F, networkstats = F, ylims=c(0,0.59), nrowmod = 2,  contrdiv = F)+theme(axis.title = element_blank())

@@

fig_thematic_div = 
  (tags(sysplots(attr(festgenrevecs,"sysdivs"), yl="Circuit thematic diversity")+
          theme(legend.position = c(0.85,0.22), legend.title = element_blank()),"A") +
  tags(divyearplot(festgenrevecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgenfests, yl="Internal thematic diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies = pies2, genrecols = sixgcols), "B") + plot_layout(widths = c(0.4,0.65))
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))

@@

tbees = 
  plotbees(festcountryvecs %>% mutate(target=indiv), "C", tlab=" Internal", col="gray50", cex=3, vw = 1.4) +
  plotbees(festcountryvecs %>% mutate(target=exdiv), "D", tlab=" Contributing", col="gray50", cex=2.9, vw=1.35)+plot_layout(nrow=2)

@@

fig_geo_div = 
  (tags(sysplots(attr(festcountryvecs,"sysdivs"), yl="Circuit geographic diversity")+
          theme(legend.position = c(0.6,0.22), legend.title = element_blank()),"A") +
  tags(divyearplot(festcountryvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exgeofests, yl="Internal geographic diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies=piesg, genrecols = sixcols), "B") + plot_layout(widths = c(0.35,0.65))
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))+
  plot_annotation(theme=theme(plot.margin=margin(0,0,0,0)))

@@

fig_lang_div = 
  (tags(sysplots(attr(festlangvecs,"sysdivs"), yl="Circuit language diversity")+
          theme(legend.position = c(0.6,0.1),legend.direction = "horizontal", legend.title = element_blank()),"A") +
  tags(divyearplot(festlangvecs  %>% mutate(target=indiv, lower=ilower, upper=iupper), 
            ex=exlangfests, yl="Internal language diversity", convert=F, splitab=F, networkstats = F, nrowmod = 2, pies=piesl, genrecols = langcols), "B")+ plot_layout(widths = c(0.4,0.65))
) /
((tbees | tdiv2 | pspacer)+plot_layout(widths = c(0.3,0.7,0), guides = "keep"))

@@

## lang centre

x= dist2(langlat, attr(festlangvecs, "latentcentre"), method="euclidean", norm="none")[,1]
names(x)=rownames(langlat)
sort(x) %>% head

# lang vs geo div?

x = festlangvecs %>% select(EventID_VZ,LibelleEvent_NEW_VZ, ab, indiv, `PFIAF category`, YearEvent) %>% left_join(festcountryvecs %>% select(EventID_VZ, indiv) %>% rename(gindiv=indiv), by="EventID_VZ")

ggplot(x, aes(indiv, gindiv, color=ab))+
  geom_point()

cor.test(x$indiv, x$gindiv)

festlangvecs %>% group_by(`PFIAF category`, ab) %>% count
xx = x %>% mutate(competitive = case_when(`PFIAF category` %in% c("Competitive Feature Film Festivals", "Competitive Specialised Feature Film Festivals") ~ "competitive", T~"noncomp"))

ggplot(xx, aes(indiv, gindiv, shape=ab, color=competitive))+
  geom_point()+
  scale_shape_manual(values=abshapes)+
  labs(x="Language internal div", y="Geo internal div")+
  geom_text(aes(label=LibelleEvent_NEW_VZ), data=xx %>%  filter(YearEvent==2019, `PFIAF category` %in% c("Competitive Feature Film Festivals")), hjust=0, size=3)

@@

## Appendix

u = umap( attr(festgenrevecs, "filmfestvecs") %>% filter(!duplicated(tmp)) %>% 
           select(starts_with("V")) # %>% ungroup() %>% mutate(V1=V1*runif(n(), 0.99,1.01 ))
           ,
           method = "umap-learn")$layout %>% 
  as.data.frame() %>% 
  cbind(attr(festgenrevecs, "filmfestvecs") %>% filter(!duplicated(tmp))  %>% select(-starts_with("V")))

u2 = u %>% mutate(colorgenre=case_when(firstfilmkind %in% mains ~ firstfilmkind, T~"others")) %>% mutate(colorgenre=fct_relevel(colorgenre, c(mains, "others")))

xcols = c(sixgcols %>% head(-1), "gray50")

g = ggplot(u2, aes(V1, V2, color=colorgenre))+
  geom_point(size=0.3)+
  scale_color_manual(values=xcols, name="")+
  theme_void()+
  theme(axis.title = element_blank(),
        legend.position = "right", legend.text = element_text(size=12),
        plot.background = element_rect(fill="white", color="gray10")
      #  panel.border  = element_rect(linewidth=0.5, color="gray10", fill=NA)
        )+
   guides(color = guide_legend(keyheight = unit(1, "lines"), override.aes = list(size = 4)))
ggsave("fig_sup_latentmap.png",g, width=10, height=7)

ggplot( aes(V1,V2,label=txtKind2, size=log(n)))+
  geom_text_repel( box.padding = 0, min.segment.length = 9999, max.time = 5, max.overlaps = 1000000)+
  scale_size(range=c(1.6,3))+
  theme_void()+
  theme(legend.position = "none",
        panel.border = element_rect(fill=NA),
        plot.background = element_rect(fill="white")
        )

ggsave("fig_sup_langmap.png", width=10, height=8, scale=0.6)
```
